Recent advances of malaria parasites detection systems based on mathematical morphology

### 2017-11-30 MDPI_template/Table.tex

	\setlength\LTleft{-0.75in}
%	\setlength\LTright{-1in}
%\small
\footnotesize
    \begin{longtable}{C{2.1cm} C{2.1cm} C{2.3cm} C{1.5cm} C{2.7cm} C{2.2cm} }
    %\begin{longtable}{|C{2cm}|c|C{2.5cm}|C{3cm}|C{2.4cm}|c|}

@@

    Anggraini \emph{et al.}, 2011 &
		- &
		thresholding + hole filling &	
		- &
		two (\emph{P.falciparum} infected and noninfected) + two life-cycle-stages &
		SE=93\% SP=99\%
        \vspace{0.6cm}
		\\
    Arco \emph{et al.}, 2014 &
		- &
		adaptive thresholding + hole filling, closing, regional minima &	
		- &
		two (infected and noninfected) &
		Acc=96.46\%
		\vspace{0.6cm}
        \\
    Das \emph{et al.}, 2011 &
		- &
		marker controlled watershed &	
		opening, closing  &
		two (infected and noninfected) &
		Acc=88.77\%
		\vspace{0.6cm}
        \\

@@

    Di Ruberto \emph{et al.}, 2002 &
		area closing, opening &
		thresholding + granulometry, watershed  transform &	
		skeleton &
		two (\emph{P.falciparum} infected and noninfected) + three life-cycle-stages &
		-
\vspace{0.6cm}
		\\

@@

    Malihi \emph{et al.}, 2013  &
    	closing &
    	-  &
    	area granulometry &
    	two (infected and noninfected) &
    	Acc=91\% SE=80\% SP=95.5\% \vspace{0.6cm} \\

@@

 Tek \emph{et al.}, 2006  &
    	- &
    	top-hat, infinite reconstruction  &
    	area granulometry &
    	two (infected and noninfected) &
    	SE=74\% SP=98\% \vspace{0.6cm} \\

    Tek \emph{et al.}, 2010  &
    	closing, granulometry &
    	thresholding + granulometry, area top-hat, closing  &
    	area granulometry &
    	five (\emph{P.falciparum}, \emph{P.vivax}, \emph{P.ovale}, \emph{P.malariae} infected, and noninfected) +
    four life-cycle-stages for species &
    	SE=72\% SP=98\% \vspace{0.6cm} \\

>>>>

%\setlength\LTleft{-0.75in}
%\setlength\LTright{-1in}
%\small
\footnotesize
\newcolumntype{H}{>{\setbox0=\hbox\bgroup}c<{\egroup}@{}}
    \begin{longtable}{C{2.1cm} C{2.1cm} C{2.3cm} H C{2.7cm} C{2.2cm} }
    %\begin{longtable}{|C{2cm}|c|C{2.5cm}|C{3cm}|C{2.4cm}|c|}

@@

    Anggraini \emph{et al.}, 2011 &
		- &
		thresholding + hole filling &	
		- &
		two (\emph{P.falciparum} infected and noninfected) + two life-cycle-stages &
		SE=93\% SP=99\%
        \vspace{0.6cm}
		\\
    Arco \emph{et al.}, 2014 &
		- &
		adaptive thresholding + hole filling, closing, regional minima &	
		- &
		two (infected and noninfected) &
		Acc=96.46\%
		\vspace{0.6cm}
        \\
    Das \emph{et al.}, 2011 &
		- &
		marker controlled watershed + opening, closing &	
		opening, closing  &
		two (infected and noninfected) &
		Acc=88.77\%
		\vspace{0.6cm}
        \\

@@

    Di Ruberto \emph{et al.}, 2002 &
		area closing, opening &
		thresholding + granulometry, watershed  transform + skeleton &	
		skeleton &
		two (\emph{P.falciparum} infected and noninfected) + three life-cycle-stages &
		-
\vspace{0.6cm}
		\\

@@

    Malihi \emph{et al.}, 2013  &
    	closing &
    	area granulometry  &
    	area granulometry &
    	two (infected and noninfected) &
    	Acc=91\% SE=80\% SP=95.5\% \vspace{0.6cm} \\

@@

 Tek \emph{et al.}, 2006  &
    	- &
    	top-hat, infinite reconstruction, area granulometry  &
    	area granulometry &
    	two (infected and noninfected) &
    	SE=74\% SP=98\% \vspace{0.6cm} \\

    Tek \emph{et al.}, 2010  &
    	closing, granulometry &
    	thresholding + granulometry, area top-hat, closing, area granulometry &
    	area granulometry &
    	five (\emph{P.falciparum}, \emph{P.vivax}, \emph{P.ovale}, \emph{P.malariae} infected, and noninfected) +
    four life-cycle-stages for species &
    	SE=72\% SP=98\% \vspace{0.6cm} \\
